---
title: "hw6.Rmd"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
```
(@) Import the data and clean appropriately. To read in the data, you can use readxl::read_xlsx('fileNameHere', sheet='sheetNameHere'). Required data are in the sheets Best in show and Best in show full sheet. Take extra care on the column names and the first few rows of the data frame after read in.

```{r}
library(tidyverse)
library(ggplot2)
best <- readxl::read_xlsx("KIB - Best in Show (public).xlsx", sheet="Best in show full sheet")
colnames(best) = best[2, ]
best <- best[-(1:3), c(1,3,5,7,41,32)]
names(best) <- c("breed", "type", "score", "popularity", "intelligence", "size")
best$type <- factor(best$type)
best$score <- as.numeric(best$score)
best$popularity <- as.numeric(best$popularity)
best$intelligence <- factor(best$intelligence)
best$size <- factor(best$size)
best <- na.omit(best)
```

(@) Create a graphics similar to the top dogs figure. Your figure need to display the following information with appropriate plotting elements:

breed of dog
type of dog (work, toy, etc.)
size of dog
data score
popularity
intelligence of the dog
appropriate legends & explanation

Hints and Notes:
The breed of dog can be displayed without the silhouttes (text only is fine)
Avoid (too much) overlap!
Choose a good color scheme.

```{r}
best <- best %>% mutate(smart = ifelse(intelligence %in% c("Above average", "Brightest", "Excellent"), TRUE, FALSE))
cols <- c("#0065ab", "#f04e8e", "#ec2121", "#c9b525", "#13650a", "#80017c", "#393a3c")
p <- best %>% ggplot(aes(x=score, y=popularity, size=size)) + geom_point(aes(shape=smart, color=type)) 
p + scale_shape_manual(values=c(60, 62)) + scale_color_manual(values=cols) + scale_size_manual(values=c(11,8,5)) + theme_bw() + geom_text(aes(x=score, y=popularity, label=breed,color=type, vjust=2), size=3.5) + scale_y_reverse() + xlim(0.98, 3.65) + guides(colour = guide_legend(override.aes = list(size=5))) + guides(shape = guide_legend(override.aes = list(size=5))) + ggtitle("Best in Show: The Ultimate Dog Data") + xlab("our data score") + theme(legend.position="top") + annotate("text", x = 1.1, y = 90, label = "The Rightly Ignored") + annotate("text", x = 1.1, y = 0, label = "Inexplicably Overrated") + annotate("text", x = 3.55, y = 90, label = "Overlooked Treasures") + annotate("text", x =3.6, y = 0, label = "Hot Dogs!")
```